---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file -->

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# tftfetch

The goal of tftfetch is to provide straightforwards functions to connect to the 
Riot API and return data in a usable format. This package focuses on endpoints
concerning the Riot game Team Fight Tactics (TFT).

## Installation

You can install the released version of tftfetch from [CRAN](https://CRAN.R-project.org){target="_blank"} with:

``` r
install.packages("tftfetch")
```

and the development version of tftfetch from [GitHub](https://github.com/){target="_blank"} with:

``` r
# install.packages("pak")
pak::pak("tidymodels/tftfetch")
```

## API Key Setup
To use `tftfetch`, you will need a Riot Games API key.

Obtain an API Key:

- Visit the [Riot Games Developer Portal](https://developer.riotgames.com/){target="_blank"}.

- Register for an account (if you don't have one).

- Go to "Dashboard" to Generate a "Development API Key" or apply for a "Production API Key" (depending on your usage needs). Note that development keys expire every 24 hours and must be refreshed.

Set Up Your `.env` File:

- It is best practice to store your API key as an environment variable to avoid hardcoding it directly into your scripts or committing it to version control (like Git).

- Create a file named .env in the root directory of your R project.

- Add your API key to this file in the following format (replace YOUR_ACTUAL_RIOT_API_KEY with the key you obtained):

``` r
RIOT_KEY=YOUR_ACTUAL_RIOT_API_KEY
```

- Ensure there are no spaces before or after the equals sign.

Load the API Key in R:

- It is recommended to us a package like `dotenv` to load this `.env` file.

- For example, including `load_dot_env()` at the beginning of your R 
scripts or R Markdown documents where you use `tftfetch` functions. This makes 
your `RIOT_KEY` available via `Sys.getenv("RIOT_KEY")`.

## Example

```{r}
#| eval: false
# First, ensure dotenv is installed: install.packages("dotenv")
library(tftfetch)
library(dotenv)

load_dot_env() # Load environment variables from your .env file
riot_key <- Sys.getenv("RIOT_KEY") # Retrieve your API key

# Example: Get account data for "Wander#HENRO" in the Americas region
get_account_by_riot_id(
  game_name = "Wander", 
  tag_line = "HENRO", 
  routing_region =  "americas", 
  api_key = riot_key
  )

# If you prefer not to save the API as a variable, you can use 
# Sys.getenv("RIOT_KEY") directly in the function
get_account_by_riot_id(..., api_key = Sys.getenv("RIOT_KEY"))
```
